%% Master CV - Christopher Gillis
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%% This master may run longer than 2 pages; tailored per-role CVs must be exactly 2.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Christopher Gillis - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Christopher}{Gillis}
\address{Tampa, FL, USA}{}{}
\phone[mobile]{813-440-7962}
\email{christopher.l.gillis@gmail.com}
\extrainfo{\href{https://linkedin.com/in/christopher-gillis-no-but-really}{LinkedIn}, \href{https://github.com/Chris-Gillis}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Senior full-stack engineer with 15+ years building reliable, scalable web and platform systems across product, data, and internal tooling. Deep across TypeScript/React, Java/Spring, Go, and Node, with a track record of improving reliability, developer productivity, and production quality in multi-tenant, distributed environments. Recent work spans AI-assisted product features, secure agent integrations (MCP with OAuth), and platform capabilities used by internal teams and external users. I take unreliable or ambiguous systems and make them dependable, end-to-end.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Languages}: Go, TypeScript/JavaScript, Python, Java, PHP.

\item \textbf{Frontend \& Backend}: React, Next.js, Angular, Inertia.js; Node/NestJS, Express, Spring Boot, Ruby on Rails, Flask/Celery, Laravel.

\item \textbf{Data \& Storage}: PostgreSQL, MySQL, Oracle; vector search (pgvector), fuzzy search (pg\_trgm), caching.

\item \textbf{Cloud \& Infrastructure}: AWS (Lambda, ECS/Fargate, RDS, S3, DynamoDB, CloudFront, SES, Cognito, VPC), Terraform, Docker, Heroku, CI/CD.

\item \textbf{Platform \& AI}: distributed \& multi-tenant systems, API design, authentication/OAuth (incl. OAuth Dynamic Client Registration), MCP clients, AI-assisted workflows (incl. Claude Code), async/job infrastructure.

\item \textbf{Integrations}: Salesforce, HubSpot, Workato, Slack.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\needspace{5\baselineskip}
\item{\cventry{2025--Present}{Software Engineer}{Agent.ai}{Remote}{}{\vspace{1pt}
\begin{itemize}
    \item Re-architected a flaky serverless AWS Lambda workflow, improving reliability and reducing related support tickets by 55\%.
    \item Built AI-assisted platform features for Agent Builder and Knowledge Builder used by 3,000+ builders.
    \item Designed a secure MCP client using OAuth Dynamic Client Registration, enabling agents to authenticate against and consume external MCP servers.
    \item Implemented HubSpot CRM integrations and AI-powered workflows enabling 100+ builders to create 250+ agents.
    \item Established frontend unit and feature testing, raising coverage from 0\% to 50\%; resolved 150+ defects across the stack.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2023--2025}{Software Engineer}{Zift Solutions (Unifyr)}{Remote}{}{\vspace{1pt}
\begin{itemize}
    \item Delivered 100+ features and fixes on a multi-tenant partner-automation platform serving 2,000+ customers.
    \item Extended Salesforce, HubSpot, and Workato integrations for automated workflows and cross-system data sync.
    \item Improved reliability and usability of a public-facing API through a rotating production support cycle.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2023--2025}{Technology Advisor}{Helmur}{Remote}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and provisioned production AWS infrastructure with Terraform (VPC, RDS, ECS/Fargate, S3, DynamoDB, CloudFront, SES, Cognito).
    \item Helped shape product roadmap, infrastructure direction, and engineering processes.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2022--2023}{Senior Software Engineer}{Spaceback}{Remote}{}{\vspace{1pt}
\begin{itemize}
    \item Led a migration from a Rails monolith to a hybrid Rails and Go services architecture.
    \item Built a caching layer for high-volume social-post data, reducing average load times by 20--25\%.
    \item Converted long-running synchronous operations into asynchronous workflows with user-facing progress tracking.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2022}{Senior Software Engineer}{OneScreen.ai}{Remote}{}{\vspace{1pt}
\begin{itemize}
    \item Led migration of the backend from Express.js to NestJS, improving maintainability and code organization.
    \item Established API contract guidelines between backend and frontend teams; conducted code reviews across a team of 8 engineers.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2019--2022}{Staff Software Engineer}{HomeCare Connect, LLC}{}{}{\vspace{1pt}
\begin{itemize}
    \item Led and mentored a team of two junior developers, providing technical direction and code reviews.
    \item Implemented a Flyway-based database migration system, eliminating error-prone manual deployment steps.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2018--2019}{Senior Associate -- Engineer}{PricewaterhouseCoopers}{}{}{\vspace{1pt}
\begin{itemize}
    \item Built a web application for structured data ingestion in a data-lake pipeline; mentored junior developers.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2014--2018}{Senior Developer}{Applied Technical Systems (USPTO)}{}{}{\vspace{1pt}
\begin{itemize}
    \item Led a reusable React component library effort, reducing duplication across multiple application teams.
    \item Served as lead front-end developer on a complex pricing-rules builder; modernized in-house testing and code coverage.
\end{itemize}}}

\vspace{3pt}

\needspace{3\baselineskip}
\item{\cventry{}{Early Career}{VBrick Systems, Masonite, HealthESystems, TechHealth}{}{}{\vspace{1pt}
C\# .NET, AngularJS, DDD/CQRS, EventStore; Java, GWT, SOAP, JUnit; Ext.js, Oracle.}}

\end{itemize}

% ============================================================
%     SELECTED PROJECTS
% ============================================================

\section{Selected Projects}
\vspace{1pt}
\begin{itemize}

\needspace{4\baselineskip}
\item{\cventry{2025--Present}{Chesscraft}{\href{https://chesscraft.ai}{chesscraft.ai}}{}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and built a full-stack SaaS platform end-to-end (React, Inertia.js, PHP/Laravel, PostgreSQL, Supabase, WASM).
    \item Built real-time features over WebSockets; implemented PostgreSQL fuzzy search (pg\_trgm) over players, openings, and game metadata.
\end{itemize}}}

\vspace{3pt}

\needspace{4\baselineskip}
\item{\cventry{2025--Present}{AoR}{\href{https://aorhq.org}{aorhq.org}}{}{}{\vspace{1pt}
\begin{itemize}
    \item Built an AI-assisted intake flow converting natural language into structured, validated requests via prompt design and output validation.
    \item Built a pgvector-backed matching and discovery system; implemented multi-role access control and an end-to-end request workflow.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2011}{B.S., Computer Science}{University of South Florida}{Tampa, FL}{}{}}

\vspace{3pt}

\item{\cventry{2007}{B.A., Psychology}{University of South Florida}{Tampa, FL}{}{}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (native).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
